### 2019-07-05 README.Rmd
commit

# Modify legend label and axis
ggmatplot(iris_sub[,c(1,3)], iris_sub[,c(2,4)], shape = c("s","S"), legend_label =  c("Sepal","Petal"), legend_title = "", xlab = "Length", ylab="Width")
```

>>>>

# Modify legend label and axis
ggmatplot(iris_sub[,c(1,3)], iris_sub[,c(2,4)], shape = c("s","S"), legend_label =  c("Sepal","Petal"), legend_title = "", xlab = "Length", ylab="Width")

# Linear regression
x <- rnorm(100,sd=2)
y <- x*0.5+rnorm(100,sd=1)
fit.y <- fitted(lm(y~x))
ggmatplot(x,cbind(y,fit.y))
```
